Product graphics

### 2009-12-05 product-graphics.tex
Add colour keys to captions where needed

\documentclass[letterpaper,oneside]{scrartcl}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{plots/}}
\usepackage{hyperref}
\usepackage{url}
\usepackage[round,sectionbib]{natbib}
\bibliographystyle{abbrvnat}
\usepackage[small]{caption2}
\usepackage[small]{titlesec}
\renewcommand\familydefault{bch}

@@

  \caption{Plots of the distribution of happiness and sex.}
  \label{fig:fact-simple}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-fluctuation}%
    \includegraphics[width=0.5\linewidth]{part-equal-area}
  \caption{Two displays of $\sim happy + health + finrela$.  (Left) Unconditional values partitioned with a vspine and fluct.  (Right) Same partitions, but health and relative financial status conditioned to uniform distribution.  We can no longer see the joint distribution of health and financial status, but it is much easier to see the conditional distribution of happiness: healthier and richer people are happier. (Maybe money does buy happiness?)}
  \label{fig:part-cond}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{sex-marital-happy}%
    \includegraphics[width=0.5\linewidth]{cascade}
  \caption{A mosaic plot of happiness by martial status and sex. (Left) Coloured by happiness.  (Right) A cascaded view helps show how the plot is built up.}
  \label{fig:cascade}
\end{figure}

@@

  \caption{(Top) Area graphics in Cartesian coordinates. (Mid) Area graphics in polar coordinates. From left to right: hbar + hbar, vspline + hbar, hspine + hspine, hspine + vspine. (Bottom) Product graphics rotated 90 degrees before being converted to polar coordinates: vbar + vbar, hspline + vbar, vspine + vspine, vspine + hspine.}

>>>>

\documentclass[letterpaper,oneside]{scrartcl}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{tikz}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{plots/}}
\usepackage{hyperref}
\usepackage{url}
\usepackage[round,sectionbib]{natbib}
\bibliographystyle{abbrvnat}
\usepackage[small]{caption}
\usepackage[small]{titlesec}
\renewcommand\familydefault{bch}

\definecolor{female}{HTML}{EF8A62}
\definecolor{male}{HTML}{67A9CF}
\definecolor{not-too-happy}{HTML}{FC8D59}
\definecolor{pretty-happy}{HTML}{FFFFBF}
\definecolor{very-happy}{HTML}{91CF60}
\definecolor{grey30}{HTML}{4D4D4D}
\newcommand{\key}[1]
  {\protect \tikz{\fill[#1] rectangle (1ex,1ex);}}

@@

  \caption{Plots of the distribution of happiness and sex (\key{male} male, \key{female} female).}
  \label{fig:fact-simple}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-fluctuation}%
    \includegraphics[width=0.5\linewidth]{part-equal-area}
  \caption{Two displays of $\sim happy + health + finrela$.  (Left) Unconditional values partitioned with a vspine and fluct.  (Right) Same partitions, but health and relative financial status conditioned to uniform distribution.  We can no longer see the joint distribution of health and financial status, but it is much easier to see the conditional distribution of happiness: healthier and richer people are happier. (Maybe money does buy happiness?).  (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy)}
  \label{fig:part-cond}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{sex-marital-happy}%
    \includegraphics[width=0.5\linewidth]{cascade}
  \caption{A mosaic plot of happiness by martial status and sex. (Left) Coloured by happiness (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy).  (Right) A cascaded view helps show how the plot is built up.}
  \label{fig:cascade}
\end{figure}

@@

  \caption{(Top) Area graphics in Cartesian coordinates. (Mid) Area graphics in polar coordinates. From left to right: hbar + hbar, vspline + hbar, hspine + hspine, hspine + vspine. (Bottom) Product graphics rotated 90 degrees before being converted to polar coordinates: vbar + vbar, hspline + vbar, vspine + vspine, vspine + hspine. (\key{male} male, \key{female} female)}
